Human Factors Influencing Visual Statistical Inference

### 2013-06-21 sociology_paper.tex
table 1 scatter plot changed

\begin{table*}[hbtp] 
\centering 
\caption{Visual test statistics used in 10 different simulation experiments. The observers are asked different questions to answer while evaluating a lineup} 
\begin{tabular}{m{.5cm}m{3cm}m{3cm}m{6.5cm}} 
\hline\hline 
Serial & Experiment & Test Statistic & Lineup question \\ [0.5ex] % inserts table %heading 
\hline 
1  & Box plot & \begin{minipage}[t]{3cm} \begin{center}	\scalebox{0.4}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} & Which set of box plots shows biggest vertical difference 
between group A and B? \\
2 &  Scatter plot & \begin{minipage}[t]{3cm}  \begin{center} \scalebox{0.45}{\includegraphics{stat_beta_k.pdf}} \end{center} \end{minipage} & Of the scatter plots below which one shows data that has steepest slope? \\

  3 & Contaminated plot &\begin{minipage}[t]{3cm} \begin{center} \scalebox{0.45}{\includegraphics{stat_contaminated.pdf}} \end{center} \end{minipage} & Of the scatter plots below which one shows data that has steepest slope? \\  \\ 
  4 & Polar vs Cartesian & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.32}{\includegraphics{stat_polar.pdf}} \end{center} \end{minipage} &Which plot is different? \\ 
  5 & Hist vs density & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.38}{\includegraphics{stat_density.pdf}} \end{center} \end{minipage} &In which plot is the blue group furthest to the right?\\ 
  6 & Violin vs boxplot & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_violin.pdf}} \end{center} \end{minipage}&  In which plot does the blue group look the most different from  the red group?\\ 
  7 & Group separation & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.4}{\includegraphics{stat_separation.pdf}} \end{center} \end{minipage} &Which of these plots has the most separation between the coloured groups?\\ 
  8 & Sine Illusion & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.28}{\includegraphics{stat_sine.pdf}} \end{center} \end{minipage} & In what picture is the size of the curve most consistent?\\ 
  9 & Gene expression &\begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.45}{\includegraphics{stat_gene.pdf}} \end{center} \end{minipage} & In which of these plots is the green line the steepest, and the spread of the green points relatively small?\\ 
  10 & Test normality & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_normality.pdf}} \end{center} \end{minipage} &Which of these plots is most different from the others?\\

@@

\cline{3-6} \cline{8-11} 
Factor & Level& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value  \\ 
  \hline
\multicolumn{2}{l}{Fixed Effect} &  &  &  &  &  & & && \\ 
&$\mu$ & 3.360 & 0.013 & 249.21 & $<$0.001 &   & -0.683 & 0.071 & -9.64 & $<$0.001 \\ 
\hline
Age ($\alpha$)& 18-25&0.000   &---  &---  &---  &  &--- &--- &---& ---\\   
 &26-30 & 0.058 & 0.013 & 4.50 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.2058 \\ 
  &31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.0376 \\ 
  &36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
  &41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.0501 \\ 
  &46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.1425 \\ 
  &above 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.0394 \\ 
  \hline
Country($\kappa$)& United States&0.000   &---  &---  &---  &  &--- &--- &---& ---\\  
  &India & 0.101 & 0.011 & 9.11 & $<$0.001 &   & 0.058 & 0.043 & 1.33 & 0.183 \\ 
  &Rest of world & -0.129 & 0.009 & -13.82 & $<$0.001 &   & 0.185 & 0.035 & 5.22 & $<$0.001 \\ 
  \hline
Education($\tau$) &High school or less&0.000   &---  &---  &---  &  &--- &--- &---& ---\\     
 &Under grad courses & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
  &Under grad degree & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.3307 \\ 
  &Graduate courses & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.1566 \\ 
  &Graduate degree & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
  \hline
Gender ($\gamma$)& Female&0.000   &---  &---  &---  &  &--- &--- &---& ---\\      
  &Male & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.50 & 0.1331 \\ 
  \hline
\multicolumn{2}{l}{Random Effect} &  &  &  &  &  & & && \\ 
& lineup($\sigma_{\ell}$) & 0.082 & 0.287 &  &  &   & 5.259 & 2.293 &  &  \\ 
 & Error($\sigma$) & 0.479 & 0.692 &  &  & & && &\\ 
   \hline
\end{tabular}
}
\label{tbl:model_result_demographics}
\end{table}

>>>>

\begin{table*}[hbtp] 
\centering 
\caption{Visual test statistics used in 10 different simulation experiments. The observers are asked different questions to answer while evaluating a lineup} 
\begin{tabular}{m{.5cm}m{3cm}m{3cm}m{6.5cm}} 
\hline\hline 
Serial & Experiment & Test Statistic & Lineup question \\ [0.5ex] % inserts table %heading 
\hline 
1  & Box plot & \begin{minipage}[t]{3cm} \begin{center}	\scalebox{0.4}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} & Which set of box plots shows biggest vertical difference 
between group A and B? \\
2 &  Scatter plot & \begin{minipage}[t]{3cm}  \begin{center} \scalebox{0.3}{\includegraphics{stat_beta_k1.png}} \end{center} \end{minipage} & Of the scatter plots below which one shows data that has steepest slope? \\

  3 & Contaminated plot &\begin{minipage}[t]{3cm} \begin{center} \scalebox{0.5}{\includegraphics{stat_contaminated.pdf}} \end{center} \end{minipage} & Of the scatter plots below which one shows data that has steepest slope? \\  \\ 
  4 & Polar vs Cartesian & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.32}{\includegraphics{stat_polar.pdf}} \end{center} \end{minipage} &Which plot is different? \\ 
  5 & Hist vs density & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.38}{\includegraphics{stat_density.pdf}} \end{center} \end{minipage} &In which plot is the blue group furthest to the right?\\ 
  6 & Violin vs boxplot & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_violin.pdf}} \end{center} \end{minipage}&  In which plot does the blue group look the most different from  the red group?\\ 
  7 & Group separation & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.4}{\includegraphics{stat_separation.pdf}} \end{center} \end{minipage} &Which of these plots has the most separation between the coloured groups?\\ 
  8 & Sine Illusion & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.28}{\includegraphics{stat_sine.pdf}} \end{center} \end{minipage} & In what picture is the size of the curve most consistent?\\ 
  9 & Gene expression &\begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.45}{\includegraphics{stat_gene.pdf}} \end{center} \end{minipage} & In which of these plots is the green line the steepest, and the spread of the green points relatively small?\\ 
  10 & Test normality & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_normality.pdf}} \end{center} \end{minipage} &Which of these plots is most different from the others?\\

@@

\cline{3-6} \cline{8-11} 
Factor & Level& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value  \\ 
  \hline
\multicolumn{2}{l}{Fixed Effect} &  &  &  &  &  & & && \\ 
&$\mu$ & 3.360 & 0.013 & 249.21 & $<$0.001 &   & -0.683 & 0.071 & -9.64 & $<$0.001 \\ 
\hline
Age ($\alpha$)& 18-25&0.000   &---  &---  &---  &  &--- &--- &---& ---\\   
 &26-30 & 0.058 & 0.013 & 4.50 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.206 \\ 
  &31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.038 \\ 
  &36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
  &41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.050 \\ 
  &46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.143 \\ 
  &above 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.039 \\ 
  \hline
Country($\kappa$)& United States&0.000   &---  &---  &---  &  &--- &--- &---& ---\\  
  &India & 0.101 & 0.011 & 9.11 & $<$0.001 &   & 0.058 & 0.043 & 1.33 & 0.183 \\ 
  &Rest of world & -0.129 & 0.009 & -13.82 & $<$0.001 &   & 0.185 & 0.035 & 5.22 & $<$0.001 \\ 
  \hline
Education($\tau$) &High school or less&0.000   &---  &---  &---  &  &--- &--- &---& ---\\     
 &Under grad courses & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
  &Under grad degree & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.331 \\ 
  &Graduate courses & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.157 \\ 
  &Graduate degree & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
  \hline
Gender ($\gamma$)& Female&0.000   &---  &---  &---  &  &--- &--- &---& ---\\      
  &Male & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.50 & 0.133 \\ 
  \hline
\multicolumn{2}{l}{Random Effect} &  &  &  &  &  & & && \\ 
& lineup($\sigma_{\ell}$) & 0.082 & 0.287 &  &  &   & 5.259 & 2.293 &  &  \\ 
 & Error($\sigma$) & 0.479 & 0.692 &  &  & & && &\\ 
   \hline
\end{tabular}
}
\label{tbl:model_result_demographics}
\end{table}

% This table had 4 digits $p$-value for last column
%\begin{table}[htbp]
%\centering
%\caption{Parameter estimates of Models \eqref{eqn:demographic_time} and \eqref{eqn:demographic_response} fitted for average log time taken and probability of correct lineup evaluations respectively. For time taken all the demographic factors are significant. For probability of correct response age group 36-40, rest of the world and graduate degree are significantly different. For gender no difference in performance is observed. Lineup variability is estimated to be very large for Model \eqref{eqn:demographic_response}.}
%\scalebox{0.86}{
%\begin{tabular}{rlrrrrrrrrrr}
%  \hline
%Demographic&& \multicolumn{4}{c} {Model \eqref{eqn:demographic_time} Log Time} & &\multicolumn{4}{c} {Model \eqref{eqn:demographic_response} Proportion Correct} \\
%
%\cline{3-6} \cline{8-11} 
%Factor & Level& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value  \\ 
%  \hline
%\multicolumn{2}{l}{Fixed Effect} &  &  &  &  &  & & && \\ 
%&$\mu$ & 3.360 & 0.013 & 249.21 & $<$0.001 &   & -0.683 & 0.071 & -9.64 & $<$0.001 \\ 
%\hline
%Age ($\alpha$)& 18-25&0.000   &---  &---  &---  &  &--- &--- &---& ---\\   
% &26-30 & 0.058 & 0.013 & 4.50 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.2058 \\ 
%  &31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.0376 \\ 
%  &36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
%  &41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.0501 \\ 
%  &46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.1425 \\ 
%  &above 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.0394 \\ 
%  \hline
%Country($\kappa$)& United States&0.000   &---  &---  &---  &  &--- &--- &---& ---\\  
%  &India & 0.101 & 0.011 & 9.11 & $<$0.001 &   & 0.058 & 0.043 & 1.33 & 0.183 \\ 
%  &Rest of world & -0.129 & 0.009 & -13.82 & $<$0.001 &   & 0.185 & 0.035 & 5.22 & $<$0.001 \\ 
%  \hline
%Education($\tau$) &High school or less&0.000   &---  &---  &---  &  &--- &--- &---& ---\\     
% &Under grad courses & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
%  &Under grad degree & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.3307 \\ 
%  &Graduate courses & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.1566 \\ 
%  &Graduate degree & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
%  \hline
%Gender ($\gamma$)& Female&0.000   &---  &---  &---  &  &--- &--- &---& ---\\      
%  &Male & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.50 & 0.1331 \\ 
%  \hline
%\multicolumn{2}{l}{Random Effect} &  &  &  &  &  & & && \\ 
%& lineup($\sigma_{\ell}$) & 0.082 & 0.287 &  &  &   & 5.259 & 2.293 &  &  \\ 
% & Error($\sigma$) & 0.479 & 0.692 &  &  & & && &\\ 
%   \hline
%\end{tabular}
%}
%\label{tbl:model_result_demographics}
%\end{table}
